Latitudinal gradients in biotic niche breadth vary across ecosystem types

### 2018-09-04 manuscript/correction.tex
reformatted correction letter following DBS comments

    We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change. After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold. However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect. Below, we present the results and the relevant portion of the discussion with the original values (struck-through) and corrected values (bold) side by side as well as the original and corrected Figures 2-3.  All supplemental figures have also been updated; as with the main-text figures below, any differences were minor. Reference numbers are as in the original main text.

@@

    Link density (mean number of feeding links per species), generality (mean
    number of prey per species), and vulnerability (mean number of predators per
    species) were strongly and positively correlated \st{($R^2$=0.891 for link
    density and generality, $R^2$\textgreater0.999 for link density and
    vulnerability, and $R^2$=0.890 for generality and vulnerability)}
    \textbf{($R^2$=0.915 for link
    density and generality, $R^2$\textgreater0.999 for link density and
    vulnerability, and $R^2$=0.912 for generality and vulnerability)}
    . Contrary
    to the expected latitudinal gradient, the best-fit version of
    equation (1) did not include a significant
    effect of latitude on species richness for any ecosystem type. Further, there were no significant
    relationships between link density, generality, or vulnerability with
    latitude for any ecosystem type.

    Each measure of specialisation increased with increasing
    species richness 
    \st{($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
    $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;}
    \textbf{($\beta_0$=0.688, $p$\textless0.001; $\beta_0$=0.658,
    $p$\textless0.001; and $\beta_0$=0.695, $p$\textless0.001, respectively;}
    Fig.~\ref{props_v_lat1}). For estuarine, marine, and terrestrial food webs the
    strength of this scaling did not vary with latitude
    \st{($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
    $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability;}
    \textbf{($\beta_{Latitude}$=-0.001, $p$=0.210 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.315 for generality; and
    $\beta_{Latitude}$=-0.001, $p$=0.205 for vulnerability;} 
    Fig.~\ref{S1}). In
    lake food webs, however, the scaling of each property was stronger towards
    the poles 
    \st{($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
    $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
    $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively)}
    \textbf{($\beta_{Latitude:Lake}$=0.003, $p$=0.031;
    $\beta_{Latitude:Lake}$=0.005, $p$=0.005; and
    $\beta_{Latitude:Lake}$=0.004, $p$=0.030, respectively)}
    . In stream food
    webs, generality increased more rapidly towards the poles
    \\\st{($\beta_{Latitude:Stream}$=0.007, $p$=0.001)}
    \textbf{($\beta_{Latitude:Stream}$=0.005, $p$=0.008)}
    while link density and
    vulnerability did not vary with latitude (i.e., the interaction term 
    $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

@@

    ... primarily gape-limited aquatic consumers tend to be more
    generalist across all types of aquatic habitats than terrestrial 
    consumers [5,53]. This trend also held in our data, although the difference between generality was not significant \st{
    $\mu_{Aquatic}$=5.47, $\mu_{Terrestrial}$=3.82; $p$=0.007 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$)} \textbf{(
    $\mu_{Aquatic}$=5.86, $\mu_{Terrestrial}$=3.75; $p$\textless0.001 for 
    \\$\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$)}.

@@

>>>>

    We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change. After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold. However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect. Below, we present the results section and the last paragraph of the discussion (the only portion to require correction) with corrected values in bold. The original and corrected values may be compared in Tables~\ref{corr_comparison} and~\ref{beta_comparison}. We also show the original and corrected Figures 2-3.  All supplemental figures have also been updated; as with the main-text figures below, any differences were minor. Reference numbers are as in the original main text.

@@

    Link density (mean number of feeding links per species), generality (mean
    number of prey per species), and vulnerability (mean number of predators per
    species) were strongly and positively correlated 
    \textbf{($R^2$=0.915 for link
    density and generality, $R^2$\textgreater0.999 for link density and
    vulnerability, and $R^2$=0.912 for generality and vulnerability; Table~\ref{corr_comparison})}
    . Contrary
    to the expected latitudinal gradient, the best-fit version of
    equation (1) did not include a significant
    effect of latitude on species richness for any ecosystem type. Further, there were no significant
    relationships between link density, generality, or vulnerability with
    latitude for any ecosystem type.

    Each measure of specialisation increased with increasing
    species richness 
    \textbf{($\beta_0$=0.688, $p$\textless0.001; $\beta_0$=0.658,
    $p$\textless0.001; and $\beta_0$=0.695, $p$\textless0.001, respectively; Table~\ref{beta_comparison}}
    Fig.~\ref{props_v_lat1}). For estuarine, marine, and terrestrial food webs the
    strength of this scaling did not vary with latitude
    \textbf{($\beta_{Latitude}$=-0.001, $p$=0.210 for link density;
    $\beta_{Latitude}$=-0.001, $p$=0.315 for generality; and
    $\beta_{Latitude}$=-0.001, $p$=0.205 for vulnerability; Table~\ref{beta_comparison};} 
    Fig.~\ref{S1}). In
    lake food webs, however, the scaling of each property was stronger towards
    the poles 
    \textbf{($\beta_{Latitude:Lake}$=0.003, $p$=0.031;
    $\beta_{Latitude:Lake}$=0.005, $p$=0.005; and
    $\beta_{Latitude:Lake}$=0.004, $p$=0.030, respectively; Table~\ref{beta_comparison})}
    . In stream food
    webs, generality increased more rapidly towards the poles
    \textbf{($\beta_{Latitude:Stream}$=0.005, $p$=0.008; Table~\ref{beta_comparison})}
    while link density and
    vulnerability did not vary with latitude (i.e., the interaction term 
    $\beta_{Latitude:Stream}$ was not retained in the best-fit models).

@@

  Importantly, while terrestrial communities are also strongly seasonal at
  high latitudes and can receive significant allochthonous
  inputs [46], terrestrial consumers tend to be
  morphologically specialised for feeding on particular prey [53].
  This means that primarily gape-limited aquatic consumers tend to be more
  generalist across all types of aquatic habitats than terrestrial 
  consumers [5, 53]. This trend also held in our data, although the difference between generality was not significant \textbf{(
    $\mu_{Aquatic}$=5.86, $\mu_{Terrestrial}$=3.75; $p$\textless0.001 for 
    $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$; Table~\ref{corr_comparison})}. 
  The key to this argument is therefore whether freshwater ecosystems experience
  more severe seasonal variation than marine and estuarine ecosystems. Although
  we are not aware of any study explicitly comparing seasonal variation in
  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
  ecosystems are indeed likely to experience more severe changes because of their small size.
  While oceans and estuaries certainly vary in terms of water temperature and
  nutrients over the course of a year [51], these changes are likely to be slower
  and milder than in freshwaters because marine and estuarine communities are buffered 
  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
  in non-marine communities [11]. Thus suggests that niche breadths may also be 
  more variable over the course of the year.

@@

\section*{Tables}

\begin{table}[h!]
\caption{Original and corrected values for correlations, mean generalities, and a student's T-test for differences in mean generalities reported in the main text. The 'Location' column indicates the section in which the relationship is described. Original values are those given in the original publication of this article. Corrected values are those obtained after correcting formatting inconsistencies in several food webs.}
\label{corr_comparison}
\small
\begin{tabular}{l l | r | r}
Relationship & Location & Original & Corrected \\
\hline
$R^2_{link density:generality}$ & Results & 0.891 & 0.915 \\
$R^2_{link density:vulnerability}$ & Results & \textgreater0.999 & \textgreater0.999 \\
$R^2_{generality:vulnerability}$ & Results & 0.890 & 0.912 \\
$\mu_{generality_{Aquatic}}$ & Discussion & 5.47 & 5.86 \\
$\mu_{generality_{Terrestrial}}$ & Discussion & 3.82 & 3.75 \\
P($\mu_{generality_{Aquatic}}>\mu_{generality_{Terrestrial}}$) & Discussion & 0.007 & \textless0.001 \\
\end{tabular}
\end{table}

\begin{table}[h!]
\caption{Original and corrected values for scaling relationships between specialisation and species richness and the effect of latitude on the strength of these relationships. Original values are those given in the original publication of this article. Corrected values are those obtained after correcting formatting inconsistencies in several food webs. All values are referred to in the Results section of the main text.}
\label{beta_comparison}
\small
\begin{tabular}{l | r r | r r}
\multirow{2}{*}{Parameter} & \multicolumn{2}{c|}{Original} & \multicolumn{2}{c}{Corrected} \\
& $\beta$ & $p$ & $\beta$ & $p$ \\
\hline
\multicolumn{5}{c}{Scaling of specialisation with species richness} \\
\hline
$\beta_{0_{link density}}$ & 0.637 & \textless0.001 & 0.688 & \textless0.001 \\
$\beta_{0_{generality}}$ & 0.553 & \textless0.001 & 0.658 & \textless0.001 \\
$\beta_{0_{vulnerability}}$ & 0.637 & \textless0.001 & 0.695 & \textless0.001 \\
\hline
\multicolumn{5}{c}{Strength of scaling and latitude: estuarine, marine, terrestrial} \\
\hline
$\beta_{{Latitude}_{link density}}$ & -0.001 & 0.365 & -0.001 & 0.210 \\
$\beta_{{Latitude}_{generality}}$ & -0.001 & 0.535 & -0.001 & 0.315 \\
$\beta_{{Latitude}_{vulnerability}}$ & -0.001 & 0.366 & -0.001 & 0.205 \\
\hline
\multicolumn{5}{c}{Strength of scaling and latitude: lakes} \\
\hline
$\beta_{{Latitude}_{link density}}$ & 0.004 & 0.019 & 0.003 & 0.031 \\
$\beta_{{Latitude}_{generality}}$ & 0.005 & 0.004 & 0.005 & 0.005 \\
$\beta_{{Latitude}_{vulnerability}}$ & 0.004 & 0.018 & 0.004 & 0.030 \\
\hline
\multicolumn{5}{c}{Strength of scaling and latitude: streams} \\
\hline
$\beta_{{Latitude}_{link density}}$ & \multicolumn{2}{c|}{NA} & \multicolumn{2}{c}{NA} \\
$\beta_{{Latitude}_{generality}}$ & 0.007 & 0.001 & 0.005 & 0.008 \\
$\beta_{{Latitude}_{vulnerability}}$ & \multicolumn{2}{c|}{NA} & \multicolumn{2}{c}{NA} \\
\end{tabular}
\end{table}
